|

### 2021-12-13 04-Chp-Systematic-Review-Results.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-results-quote)', echo = TRUE}
Hold  
```

@@

Using the methods outlined in the previous chapter, here I present  the results of a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, it examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes

@@

(ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process. The different contributions of standard bibliographic databases and preprint servers to the review are indicated.

@@

<!----------------------------------------------------------------------------->
(ref:agreeInter-caption) Inter-rater agreement on a subset of records, indicating high accuracy.

@@

<!----------------------------------------------------------------------------->
(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.

@@

(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design. Note that three studies reported on multiple analytical designs within a single study report (Beydoun 2011,[@beydoun2011] Reitz 2010,[@reitz2010] and Benn 2017[@benn2017]), and these have been duplicated across the relevant sub-sections. Preprinted studies are denoted using an asterik.

@@

(ref:cohortLocations-cap) Geographical distribution of study cohorts

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia

(ref:obsHyperDementia-scap) Meta-analysis of hypercholesterolemia on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsDementia-cap) Random-effects meta-analysis of four lipid fractions (total cholesterol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction. Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts within a single study and the results for each cohort are presented separately here.

(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of four lipid fractions on all-cause dementia
```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
```
<!----------------------------------------------------------------------------->

@@

(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statins on all-cause dementia. D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the RoB2 tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond in each forest plot presented above.

(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia

(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease

(ref:obsHyperAD-scap) Meta-analysis of hypercholesterolemia on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsAD-cap)  Random-effects meta-analysis of four lipid fractions (total cholesterol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction. Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts within a single study and the results for each cohort are presented separately here.

(ref:lipidFractionsAD-scap) Random-effects meta-analysis of four lipid fractions on Alzheimer's disease

@@

Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)). However, all of these studies took a two-sample approach, making use of summary statistics from the Global Lipid Genetics Consortium (GLGC) and International Genomics of Alzheimer's Project (IGAP) consortia. Synthesis of these results would would result in a falsely precise estimate caused by multiple counting of the same participants,and as a result, no meta-analysis of these studies was performed.

However, across each analysis using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).

<!----------------------------------------------------------------------------->
(ref:mrDuplication-cap) Summary of duplication across Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP). Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.

(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease

@@

<!----------------------------------------------------------------------------->
(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease

(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease

```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia

(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.

@@

```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinVaD-cap) Random-effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia

@@

```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
```
<!----------------------------------------------------------------------------->

@@

<!-- TODO Add legend to this figure so that it is clear what the lines are - YBS was confused -->

<!----------------------------------------------------------------------------->
(ref:lipidsDoseResponse-cap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease

(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol

@@

Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found weak evidence for variation in the observed effect estimates due to these factors.

@@

<!----------------------------------------------------------------------------->
(ref:typeByYear-cap) Included study designs for any dementia outcome by year of publication

@@

(ref:mrAssumptions-cap) Summary of the assumptions in Mendelian randomisation analyses: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e. there is no horizontal pleiotropy).

(ref:mrAssumptions-scap) Overview of assumptions in Mendelian randomisation analyses

@@

(ref:preprintGrowth-cap) Growth of preprint repositories over time. Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv N = `r n_at_search["bio"]`, medRxiv N = `r n_at_search["med"]`), the number of hits returned by each is expected.

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-results-quote)', echo = TRUE}
Hold  
```

@@

Using the methods outlined in the previous chapter, here I present  the results of a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, it examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes.

@@

(ref:prisma-flow-cap) __PRISMA flow diagram__ - The diagram illustrates how records moved through the systematic review process. Note that the different contributions of standard bibliographic databases (left) and preprint servers (right) to the review are indicated.

@@

<!----------------------------------------------------------------------------->
(ref:agreeInter-caption) __Inter-rater agreement__ - For a subset of records, the decisions between two independent were compared. Gewt's $AC1$ was calculated from this data to assess inter-rater reliability, indicating high accuracy ($AC1$ = `r agreeInter_coeff[1]`).

@@

<!----------------------------------------------------------------------------->
(ref:agreeIntra-caption) __Intra-rater agreement__ - For a subset of records, the decisions between the same reviewer with 3 month lag were compared. Gewt's $AC1$ was calculated from this data to assess intra-rater reliability, indicating high consistency ($AC1$ = `r agreeIntra_coeff[1]`).

@@

(ref:studyCharacteristics-caption) __Characteristics of included studies__ - The characteristics of studies included in this review, stratified by study design, are presented below. Note that three studies reported on multiple analytical designs within a single study report (Beydoun 2011,[@beydoun2011] Reitz 2010,[@reitz2010] and Benn 2017[@benn2017]), and these have been duplicated across the relevant sub-sections. Preprinted studies are denoted using an asterik.

@@

(ref:cohortLocations-cap) __Geographical distribution of study cohorts__ - The country or countries of origin for the studies include in the review are shown below. Note that the majority of included studies were performed in the Western world, predominantly in Europe and North America.

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperDementia-cap) __Random-effects meta-analysis of hypercholesterolemia on all-cause dementia__ - Non-randomised studies examining the association of hypercholesterolemia with all-cause dementia were synthesised using a random-effects meta-analysis. Subgroup estimates, stratified by overall risk-of-bias level, are also presented. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

(ref:obsHyperDementia-scap) Random-effects meta-analysis of hypercholesterolemia on all-cause dementia

@@

\newpage
\thispagestyle{empty}

<!----------------------------------------------------------------------------->
(ref:lipidFractionsDementia-cap) __Random-effects meta-analysis of lipids on all-cause dementia__ - Non-randomised studies examining the association of four lipid fractions (total cholesterol, HDL, LDL, and triglycerides) with all-cause dementia risk, standardised per 1-SD increase, were synthesised using a random-effects meta-analysis. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond. Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts and these are presented separately.

(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of lipids and all-cause dementia

```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
```
<!----------------------------------------------------------------------------->

@@

(ref:statinsRCT-cap) __Random-effects meta-analysis of statins on all-cause dementia in RCTs__ - 
Randomised controlled trials examining the effect of statin use on all-cause dementia risk were synthesised using a random-effects meta-analysis. D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the RoB2 tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia in RCTs

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinDementia-cap) __Random-effects meta-analysis of statins on all-cause dementia__ - Non-randomised studies examining the association of statin use with all-cause dementia were synthesised using a random-effects meta-analysis. Subgroup estimates, stratified by overall risk-of-bias level, are also presented. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-I tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

@@

<!----------------------------------------------------------------------------->
(ref:obsFibrateDementia-cap) __Random-effects meta-analysis of fibrates on all-cause dementia__ - Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-I tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

(ref:obsFibrateDementia-scap) Random-effects meta-analysis of fibrates on all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperAD-cap) __Random-effects meta-analysis of hypercholesterolemia on Alzheimer's disease__ - Non-randomised studies examining the association of hypercholesterolemia with Alheimer's disease were synthesised using a random-effects meta-analysis. Subgroup estimates, stratified by overall risk-of-bias level, are also presented. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

(ref:obsHyperAD-scap) Random-effects meta-analysis of hypercholesterolemia on Alzheimer's disease

@@

\newpage
\thispagestyle{empty}

<!----------------------------------------------------------------------------->
(ref:lipidFractionsAD-cap)  __Random-effects meta-analysis of association of lipid fractions with Alzheimer's disease__ - D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond. Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts and these are presented separately.

(ref:lipidFractionsAD-scap) Random-effects meta-analysis of lipids on Alzheimer's disease

@@

Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)). However, all of these studies took a two-sample approach, making use of summary statistics from the Global Lipid Genetics Consortium (GLGC) and International Genomics of Alzheimer's Project (IGAP) consortia. Synthesis of these results would would result in a falsely precise estimate caused by multiple counting of the same participants,and as a result, no meta-analysis of these studies was performed. However, across each analysis using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).

<!----------------------------------------------------------------------------->
(ref:mrDuplication-cap) __Summary of duplication across two-sample Mendelian randomisation studies__ - Several Mendelian randomisation studies used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP). Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.

(ref:mrDuplication-scap) Summary of duplication across two-sample Mendelian randomisation studies

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinAD-cap) __Random-effects meta-analysis of statins on Alzheimer's disease__ Non-randomised studies examining the association of statin use with Alzheimer's disease were synthesised using a random-effects meta-analysis. Subgroup estimates, stratified by overall risk-of-bias level, are also presented. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-I tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:mrStatinAD-cap) __Random-effects meta-analysis of HMGCR inhibition on Alzheimer's disease__ - Mendelian randomisation studies examining the association of genetically lowered LDL-c via HMGCR inhibition with Alzheimer's were synthesised using a random-effects meta-analysis. D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the Mamluk _et al_ tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

(ref:mrStatinAD-scap) Random-effects meta-analysis of HMGCR inhibition on Alzheimer's disease

```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
```
&nbsp;<!----------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:obsHyperVaD-cap) __Random-effects meta-analysis of hypercholesterolemia on vascular dementia__ - Non-randomised studies examining the association of hypercholesterolemia with vascular dementia were synthesised using a random-effects meta-analysis. Subgroup estimates, stratified by overall risk-of-bias level, are also presented. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

(ref:obsHyperVaD-scap) Random-effects meta-analysis of hypercholesterolemia on vascular dementia

@@

<!----------------------------------------------------------------------------->
(ref:lipidFractionsVaD-cap) __Random-effects meta-analysis of total cholesterol on vascular dementia__ - Non-randomised studies examining the association of total cholesterol with vascular dementia risk, standardised per 1-SD increase in the lipid fraction, were synthesised using a random-effects meta-analysis. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

@@

```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsVaD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsVaD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:obsStatinVaD-cap) __Random-effects meta-analysis of statins on vascular dementia__ - Non-randomised studies examining the association of statin use with vascular dementia were synthesised using a random-effects meta-analysis. Subgroup estimates, stratified by overall risk-of-bias level, are also presented. D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-I tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.

@@

```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinVaD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
```
<!----------------------------------------------------------------------------->

@@

<!-- TODO Improve caption for the legend below -->

<!----------------------------------------------------------------------------->
(ref:lipidsDoseResponse-cap) __Dose-response meta-analysis of total cholesterol on Alzheimer's disease__ - Non-randomised studies examining the association of lipids levels with Alzheimer's disease across several categories or "doses" of exposure were synthesised using a dose response meta-analysis. The reference dose was defined _a priori_ as 200 _mg/dL_, the cut-off of the "Normal"/"Optimal" category for total cholesterol as detailed in Table \@ref(tab:lipidLevels-table).

(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease

@@

Age and gender were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found weak evidence for variation in the observed effect estimates due to these factors.

@@

<!----------------------------------------------------------------------------->
(ref:typeByYear-cap) __Study designs by year of publication__ - Included studies across all dementia outcomes are shown grouped by study design and year of publication. Note that Mendelian randomisation studies only begin to appear in the evidence base much later than other study designs.

@@

(ref:mrAssumptions-cap) __Summary of the assumptions in Mendelian randomisation analyses__ - Mendelian randomisation analyses make three key assumptions: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e. there is no horizontal pleiotropy).

(ref:mrAssumptions-scap) Summary of the assumptions in Mendelian randomisation analyses

@@

(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv N = `r n_at_search["bio"]`, medRxiv N = `r n_at_search["med"]`), the number of hits returned by each is expected.

### 2021-12-13 05-Chp-CPRD-Analysis.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion

<!----------------------------------------------------------------------------->
(ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record. Note that an outcome of "probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.

@@

(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panel B).

(ref:immortalTimeBias-scap) shortcap

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:negativeOutcome-cap) Causal diagram (directed acyclic graph) showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$. Note the absence of any arrow between $X$ and $N$. In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders $U$ (assuming $C$ has been adjusted for).

@@

<!--------------------------------------------------------------------------->
(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. The largest cause of attrition was the absence of an index event of interest.

@@

<!--------------------------------------------------------------------------->
(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.

@@

<!----------------------------------------------------------------------------->
(ref:completeCaseFig-cap) Comparison of analyses using the complete case versus imputed cohorts.

@@

>>>>

<!----------------------------------------------------------------------------->
(ref:decisionTreeFig-cap) __Decision tree for assigning dementia subtypes__ - Based on the presence of specific Read codes in the patient's record, a decision tree was used to classify dementia subtypes ("Probable" or "Possible" Alheimer's disease, vascular dementia, and other dementia). Note that an outcome of "probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.

@@

(ref:immortalTimeBias-cap) __Immortal time bias__ - The two presentations of immortal time bias are illustrated. Panel A shows the selection bias presentation, where time prior to a statin exposure is excluded from the analysis and outcomes in this time period are lost. Panel B shows the misclassification presentation, there time (and events) prior to statin exposure is incorrectly assigned to the exposed group.

(ref:immortalTimeBias-scap) Immortal time bias

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:negativeOutcome-cap) __Causal diagram for ideal negative outcome__ - The directed acyclic graph shows the relationship between the exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$. Note the absence of any arrow between $X$ and $N$. In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders $U$ (assuming $C$ has been adjusted for).

@@

<!--------------------------------------------------------------------------->
(ref:cprdFlowchart-cap) __Attrition of CPRD participants__ - Patients were excluded from the study cohort for several reasons, and the number of patients excluded as each eligibility criterion was applied is shown above. Note that the largest cause of attrition was the absence of an index event of interest.

@@

<!--------------------------------------------------------------------------->
(ref:cprdPrimary-cap) __Results from primary analyses of CPRD data__ - Effect estimates obtained from the fully-adjusted time-varying model with participant age as the time scale, stratified by lipid-regulating agent and dementia outcome.

@@

<!----------------------------------------------------------------------------->
(ref:completeCaseFig-cap) __Complete case vs. imputed data analysis__ Comparison of analyses using the complete case versus imputed cohorts, indicating broad agreement between the two approaches. Note that the analyses using imputed data gave more precise estimates due to the low proportion of patients with complete covariate data.

@@

#### Impact of additional covariates {#cprd-impact-additional-covar}
